Paper_analyses

### 2022-02-08 Paper_Analyses_subj_obje_arousal.Rmd
recover  accidentally discarded changes

clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,4,6,7,8,9,10)]
res.mfa_bio_vs_self<- FactoMineR::MFA(clustering_new_pre_PCA3.1, 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

```{r}
# use stim as indicator
colnames(clustering_new_pre_PCA3)
clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,6,7,8,9,10)]

res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,2:7], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

@@

clustering_new_pre_PCA3.1.scale$stim_descr
res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

@@

@@

here

@@

```{r}
colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
               group = c(1, 3, 3, 3), 
               type = c("n", "s", "s", "s"),
               name.group = c("ssid","pupil","HR","SCR"),
               num.group.sup = c(1),
               graph = TRUE)

>>>>

clustering_new_pre_PCA3$AR
clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,4,6,7,8,9,10)]
res.mfa_bio_vs_self<- FactoMineR::MFA(clustering_new_pre_PCA3.1, 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

```{r}
# use stim as indicator
colnames(clustering_new_pre_PCA3)

clustering_new_pre_PCA3$val_cut_iaps<- cut(clustering_new_pre_PCA3$ValenceMean, 3, labels = 
                                             c("neg", "mid", "pos"))

clustering_new_pre_PCA3$aro_cut_iaps<- cut(clustering_new_pre_PCA3$ArousalMean, 3, labels = 
                                             c("low", "mid", "high"))
clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,22,23,6,7,8,9,10)]
colnames(clustering_new_pre_PCA3.1)

res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,1:9], 
               group = c(4, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

@@

clustering_new_pre_PCA3.1.scale$stim_descr

clustering_new_pre_PCA3.1.scale
res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

dimdesc(res.mfa_bio_vs_self2_scale)

TInPosition::
```

```{r}
# get_eigenvalue(res.mfa): Extract the eigenvalues/variances retained by each dimension (axis)
eig.val_bui_self_scl <- get_eigenvalue(res.mfa_bio_vs_self2_scale)
head(eig.val_bui_self_scl)

# The function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:

fviz_screeplot(res.mfa_bio_vs_self2_scale)

group_bio_self_scl <- get_mfa_var(res.mfa_bio_vs_self2_scale, "group")
group_bio_self_scl

# Coordinates of groups
options(scipen = 999)
head(group_bio_self_scl$coord)

#    Dim.1      Dim.2      Dim.3     Dim.4        Dim.5
# auton 0.5042850 0.98835343 0.85875961 0.4433362 0.0008990348
# subj  0.6790127 0.00720065 0.01629939 0.3014437 0.2019402875

head(group_bio_self_scl$cos2) 
# Cos2: quality of representation on the factore map

#        Dim.1         Dim.2        Dim.3      Dim.4           Dim.5
# auton 0.09726538 0.37362051551 0.2820651231 0.07517484 0.0000003091428
# subj  0.44230732 0.00004974068 0.0002548654 0.08717275 0.0391213886164

# Contributions to the  dimensions
head(group_bio_self_scl$contrib)

#          Dim.1      Dim.2     Dim.3   Dim.4      Dim.5
# auton 42.61692 99.2767194 98.137338 59.5258  0.4432251
# subj  57.38308  0.7232806  1.862662 40.4742 99.5567749

# draw a bar plot of groups contribution to the dimensions

# Contribution to the first dimension
fviz_contrib(res.mfa_bio_vs_self2_scale, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_bio_vs_self2_scale, "group", axes = 2)
# basically they are contibuting to separate dimensions

# is this improved if we dropping pupil?

# res.mfa_bio_vs_self2_scale_nopup<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,c(2, 4,6:7)], 
#                group = c(1, 1, 2), 
#                type = c("n", "s", "s"),
#                # "s", "s", "s"
#                name.group = c("pp_stim","auton","subj"),
#                num.group.sup = c(1),
#                # ind.sup = c(1,2),
#                graph = TRUE)
# 
# 
# # Contribution to the first dimension
# fviz_contrib(res.mfa_bio_vs_self2_scale_nopup, "group", axes = 1)
# # Contribution to the second dimension
# fviz_contrib(res.mfa_bio_vs_self2_scale_nopup, "group", axes = 2)
# basically they are contibuting to separate dimensions

#
# is this improved if we dropping pupil? almost but not really

# head(res.mfa_bio_vs_self2_scale_nopup$global.pca)

?dimdesc
probabchecl<- dimdesc(res.mfa_bio_vs_self2_scale, axes = 1:2, proba = .05)

quantitative variables
```{r}
quanti.var_bio_vs_self2_scale <- get_mfa_var(res.mfa_bio_vs_self2_scale, "quanti.var")
quanti.var_bio_vs_self2_scale

# Correlation between quantitative variables and dimensions.
# corrwlation circle

??factoextra::fviz_mfa_var

res.mfa_bio_vs_self2_scale
fviz_mfa_var(res.mfa_bio_vs_self2_scale, 
             "quanti.var", 
             palette = "jco", 
             col.var.sup = "violet", 
             repel = TRUE,
              addEllipses = TRUE,
             legend = "bottom",
              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             col.var = "contrib" )

fviz_mfa_var(res.mfa_bio_vs_self2_scale, "quanti.var", col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"))

# Contributions to dimension 1
fviz_contrib(res.mfa_bio_vs_self2_scale, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")

fviz_contrib(res.mfa_bio_vs_self2_scale, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

```
Graph of individuals  = rows
```{r}
fviz_mfa_ind(res.mfa_bio_vs_self2_scale, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

clustering_new_pre_PCA3.1.scale$stimDescription
??fviz_mfa_ind
fviz_mfa_ind(res.mfa_bio_vs_self2, 
             habillage = "aro_cut_iaps", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),

             ellipse.type = "confidence", 
             # geom = c("point"),
             alpha.ind = .2,
             addEllipses = TRUE, 
             repel = TRUE # Avoid text overlapping
             )

fviz_mfa_ind(res.mfa_bio_vs_self2, 
             habillage = "stimDescription", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),

             ellipse.type = "confidence", 
             # geom = c("point"),
             alpha.ind = .2,
             addEllipses = TRUE, 
             repel = TRUE # Avoid text overlapping
             )

fviz_mfa_ind(res.mfa_bio_vs_self2, 
             habillage = "ssid", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),

             ellipse.type = "confidence", 
             # geom = c("point"),
             alpha.ind = .0,
             addEllipses = TRUE, 
             repel = TRUE # Avoid text overlapping
             )

```{r}
fviz_ellipses(res.mfa_bio_vs_self2, c("val_cut_iaps"), repel = TRUE)

# Graph of partial individuals
The results for individuals obtained from the analysis performed with a single group are named partial individuals. In other words, an individual considered from the point of view of a single group is called partial individual.

The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
```{r}

fviz_mfa_ind(res.mfa_bio_vs_self2, partial = "all")

fviz_mfa_ind(res.mfa, 
             partial = c("1neg", "1pos"))

fviz_mfa_axes(res.mfa)

# install.packages()

install.packages("MExPosition")
```

@@

```
Agg within participant by neg pos etc (using normative data)
With and without selfreports

```{r}
?cut
#create valence categories based ion self reports (IAPS validation)
clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))

# scale within subject
# aggregate by subject and

View(clustering_new_pre_PCA3_val_vat)
# clustering_new_pre_PCA3_val_vat%>%
#   group_by(ssid)%>%
#   mutate_if(is.numeric, scale)

clustering_new_pre_PCA3_val_vat_agg<- clustering_new_pre_PCA3_val_vat%>%
  group_by(ssid, valence_iaps_cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

colnames(clustering_new_pre_PCA3_val_vat_agg)
clustering_new_pre_PCA3_val_vat_agg[,c(2,5,6,7,8,9)]

FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("ss_id_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# scale
clustering_new_pre_PCA3_val_vat_agg_scale<- clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)]

clustering_new_pre_PCA3_val_vat_agg_scale%>%
   # group_by(ssid)%>%
  mutate_if(is.numeric, scale)

clustering_new_pre_PCA3_val_vat_scale_then_agg<- clustering_new_pre_PCA3_val_vat%>%
  group_by(ssid)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(ssid, valence_iaps_cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3_val_vat_scale_then_agg1<- clustering_new_pre_PCA3_val_vat_scale_then_agg[,c(1:2, 5:9)]

?FactoMineR::MFA
res.mfa_val_cat_scal<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               name.group = c("ss_id_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

fviz_mfa_ind(res.mfa_val_cat_scal, 
             habillage = "valence_iaps_cat", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, 
             ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

# we can sorta see that while things allign relativelly well on sujective dimension, they don't allugn very well on the autonomic dimension

@@

@@

```{r}
colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)

View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
               group = c(1, 3, 3, 3), 
               type = c("n", "s", "s", "s"),
               name.group = c("ssid","pupil","HR","SCR"),
               num.group.sup = c(1),
               graph = TRUE)
